Response to Referees

### 2025-06-25 ms/submission/AuthorComments-egusphere-2025-1046.qmd
address RC1.2, RC1.3, RC2.2

@@

@@

@@

## Specifics Comments

>>>>

Thank you for your positive comments on the article and for your suggestions to improve its readability. We have taken your advice to review the article for conciseness and have made several changes to reduce its length, while retaining the key details of the modelling methodology. In particular, we have removed the sections on peatland extent mapping, which was not central to the main focus of the study, and we have shortened some of the other sections as well. We have moved some of the more detailed descriptions of the methodology to the appendix, to make the main text more accessible and focused.

@@

Thank you for this advice and the specific examples you provided. We have gone through the manuscript and revised the language to make it more formal and scientific, while aiming to retain clarity and accessibility.

@@

Thank you for raising this concern. We address the specific comments on this theme below, and believe that our responses show why we disagree that there are fundamental errors in the methods. For the same reasons outlined below, we do not think that the conclusion the title alludes to is biased.

@@

Thank you for your positive comments on the research and title, and for your suggestions to improve the writing style. We have gone through the manuscript and revised the language to make it more formal and scientific, while aiming to retain clarity and accessibility. We have also tried to reduce jargon where possible, while retaining the necessary technical terms.
